RESEARCH PROPOSAL

### 2022-05-24 papers/fuzzy-fmt/OralExm-researchproposal.tex
OralExm edits

\section{Part 2: Research Done}
We have a working model of a soft-sphere reference fluid that depends 
on a smooth potential function instead of on the discontinuous hard-sphere potential 
which has been the standard in use for the last fifty years. 
In our paper prepared for publication we have: \\
$\bullet$ Demonstrated good agreement between our WCA fluid and Barker-Henderson fluid \\
$\bullet$ Demonstrated good agreement between our WCA fluid and Monte-Carlo simulations \\
$\bullet$ Demonstrated good agreement between our WCA fluid and experiments with Argon \\

\section{Part 3: Research To Do}
\noindent Toward a better model and a better understanding of our model, I propose to: \\
$\bullet$ Find the internal energy for our WCA fluid model \\
$\bullet$ Improve results at low temperature, high density \\ %pressure calculations  \\
%$\bullet$ Possibly derive temperature-dependent parameter with B3 and B2  \\
%4- another functional for better pressure in freezing with improved pressure calculation\\
%4- another function (instead of Verf) for better pressure in freezing \\
$\bullet$ Examine and demonstrate the generality and usefulness of our 
method by applying it to other soft repulsive fluid potentials (Dr. Roundy famous!) \\
%$\bullet$ Apply our model  (ie. show by example) to demonstrate usefulness \\ %and market \\
%better understand and meet the needs of those who would benefit from our approach and market \\

>>>>

\section{Part 2: Research Done}
We have a working model of a soft-sphere reference fluid that depends 
on a smooth potential function instead of on the discontinuous hard-sphere potential 
which has been the standard in use for the last fifty years. 
In our paper prepared for publication we have: \\
$\bullet$ Demonstrated good agreement between our WCA fluid and Barker-Henderson fluid \\
$\bullet$ Demonstrated good agreement between our WCA fluid and Monte-Carlo simulations \\
$\bullet$ Demonstrated good agreement between our WCA fluid and experiments with Argon under high pressure (so attractive forces can be ignored) \\

\section{Part 3: Research To Do}
\noindent %Toward a better model and a better understanding of our model, 
I propose some possible paths for wrapping up my research: \\
$\bullet$ Finish up the paper we have and graduate. \\
$\bullet$ Write a follow-on paper and graduate. In a second paper, I would 
like to look at finding the internal energy for our WCA fluid model using 
classical Density Functional Theory and our SFMT functional 
for the Helmholtz free energy that we developed in our first paper 
\begin{align}
  U[n(\vec r), s(\vec r)] = F[n(\vec r)] + T\int s(\vec r)
\end{align}
 If more is needed, or time allows, I could also: \\
$\bullet$ Look at how to improve results at low temperature, high density 
by adjusting our functional and/or potential and our pressure calculations.\\ %pressure calculations  \\
%$\bullet$ Possibly derive temperature-dependent parameter with B3 and B2  \\
%4- another functional for better pressure in freezing with improved pressure calculation\\
%4- another function (instead of Verf) for better pressure in freezing \\
$\bullet$ Examine and demonstrate the generality and usefulness of our 
method by applying it to other soft repulsive fluid potentials (Dr. Roundy famous!) \\
%$\bullet$ Apply our model  (ie. show by example) to demonstrate usefulness \\ %and market \\
%better understand and meet the needs of those who would benefit from our approach and market \\
